### 2025-03-01 tutorials/getstarted.qmd
Improve technical details print.

```{julia}
#| code-fold: true
#| echo: false
using Pkg
Pkg.status()
```
```{julia}
#| code-fold: true
#| echo: false
using Dates
println("This tutorial was last rendered $(now())");
```

>>>>

```{julia}
#| code-fold: true
#| echo: false
using Pkg
Pkg.status()
```
```{julia}
#| code-fold: true
#| echo: false
#| output: asis
using Dates
println("This tutorial was last rendered $(Dates.format(now(), "U d, Y, H:M:S")).");
```
